\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}
\newcommand{\SubItem}[1]{
	{\setlength\itemindent{15pt} \item[-] #1}
}
\title{Anime Recommendation System Through a Discord Bot\\
{\footnotesize \textsuperscript{}Programming Project: Unit 4}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Saulo Acevedo}
\IEEEauthorblockA{JSAcevedo2000\\
js.acevedo2000@gmail.com}
\and
\IEEEauthorblockN{Carolina Garma}
\IEEEauthorblockA{TokiYomi\\
tokiyomi@hotmail.com}
\and
\IEEEauthorblockN{Guillermo Montes de Oca}
\IEEEauthorblockA{MontesdeOcaG\\
kruang@mail.me}
}

\maketitle

\begin{abstract}
This document is a model and instructions for \LaTeX.
This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
or Math in Paper Title or Abstract.
\end{abstract}

\begin{IEEEkeywords}
component, formatting, style, styling, insert
\end{IEEEkeywords}

\section{Introduction}
Nowadays, data science has crowned itself as one of the most-popular disruptive technologies, and its mainly focused on Artificial Intelligence or Data Mining, both being data-based tasks with a lot of usefulness in what we know today as the fourth industrial revolution: enormous amounts of information (<big data>) are produced each second, and it is necessary to find out the value behind each kilobyte of it; whether it is for decision-making in big companies or for our virtual assistant to know if it is going to rain in the evening \cite{b1}.  

As it happens with all the new technologies being developed, data science also has an “underground” side, a side which even though it is an important application of it and it is present in popular websites and online services, we may not notice it: recommendation systems. Those algorithms which suggest you buy a mouse-pad to complement the new mouse you are ordering from Amazon, or those which make appear an advertisement of that new video-game you just were talking about with your friend \cite{b2}. 

Recommendation systems may seem easy to develop but they could not be more complicated, as it is necessary to take in consideration many factors: from what are we trying to recommend (movies, products, food, places…), going through which and how much data do we have (reviews, scores, names, locations…) and even to who the recommendation is aimed (a teenager aged 16-18 who lives in the south of Merida, a woman who is checking the prices of flights to Cancun or a programming teacher who likes videogames) \cite{b3}.

Either we are trying to obtain content or user-based recommendations, the math behind a simple system of this type rely on probability and statistics: depending on the complexity, accuracy and amount of data available to use, our mathematical procedure will be more or less complicated, always based on matrix operations and correlations \cite{b4}. All in all, these systems only seek to make the life of the user a bit simpler by “choosing for them”, and sometimes trying to obtain a profit from that automatized selection \cite{b5}.

\section{Motivation}
In modern society people have too many options to choose in many aspects of daily life: clothing, eating, reading, listening, watching, playing, and many other actions we do everyday now offer a wide variety and let the user decide what he/she wants to do. For this new (and kind of unlimited) selection of possibilities, a recommender system which takes as base data previously provided by a determined user and returns a customized recommendation for any of those tasks, can indeed make our lives a little bit easier.

Taking in consideration the advantages of Recommendation Systems, we seek to build one and adapt it to a field which we like, and where it has not been applied yet: anime (“Japanese animation”). Even if there are services such as Netflix or Spotify which have this type of algorithms and use them for series, movies or music, it still not applied to anime series in a way that it is accessible to the user and easy to use.

Crunchyroll could be mentioned as an online service of anime streaming with a recommendation system, however, its system is based on an item-item approach: it is not personalized for each user and instead it offers predetermined suggestions for each anime \cite{b6}. Having a content-based approach based on similarities between anime series and scores given by users may result in more accurate recommendations.

\section{Objective}
\begin{itemize}
	\item Develop two Anime Recommendation Systems (A.R.S) from a dataset obtained at Kaggle \cite{b7}, through different approaches:
	\SubItem A collaborative approach: according to an input (the name of an anime) provided by the user, it will suggest other similar anime series to watch (depending on the score given by other users).
	\SubItem A content-based approach: according to an input (scores of different anime genres) provided by the user, it will suggest other anime series to watch which may be similar in genre (it could also apply for studios, directors, producers, etc.).
\end{itemize}

\section{Problem Description}

Taking in consideration the advantages of Recommendation Systems, we seek to build one and adapt it to a field which we like, and where it has not been applied yet: anime (“Japanese animation”). Even if there are services such as Netflix or Spotify which have this type of algorithms and use them for series, movies or music, it still not applied to anime series in a way that it is accessible to the user and easy to use.

\section{Proposed Solution}

Taking in consideration the advantages of Recommendation Systems, we seek to build one and adapt it to a field which we like, and where it has not been applied yet: anime (“Japanese animation”). Even if there are services such as Netflix or Spotify which have this type of algorithms and use them for series, movies or music, it still not applied to anime series in a way that it is accessible to the user and easy to use.

\section{Results}

Taking in consideration the advantages of Recommendation Systems, we seek to build one and adapt it to a field which we like, and where it has not been applied yet: anime (“Japanese animation”). Even if there are services such as Netflix or Spotify which have this type of algorithms and use them for series, movies or music, it still not applied to anime series in a way that it is accessible to the user and easy to use.

\begin{thebibliography}{00}
\bibitem{b1} Lin, K. (2019). “Role of Data Science in Artificial Intelligence”. Retrieved from: https://towardsdatascience.com/role-of-data-science-in-artificial-intelligence-950efedd2579
\bibitem{b2} Madamasy, M. (2019). “Introduction to recommendation systems and How to design them, that resembling the Amazon”. Retrieved from: https://medium.com/@madasamy/introduction-to-recommendation-systems-and-how-to-design-recommendation-system-that-resembling-the-9ac167e30e95
\bibitem{b3} Kordík, P. (2018). “Machine Learning for Recommender systems — Part 1 (algorithms, evaluation and cold start)”. Retrieved from: https://medium.com/recombee-blog/machine-learning-for-recommender-systems-part-1-algorithms-evaluation-and-cold-start-6f696683d0ed
\bibitem{b4} Rocca, B. (2019). “Introduction to recommender systems”. Retrieved from: https://towardsdatascience.com/introduction-to-recommender-systems-6c66cf15ada
\bibitem{b5} Mall, R. (2019). “Recommender System”. Retrieved from: https://towardsdatascience.com/recommender-system-a1e4595fc0f0
\bibitem{b6} Crunchyroll Forum. (2018). “Better Recommendation System”. Retrieved from: https://www.crunchyroll.com/forumtopic-944365/better-recommendations-system
\bibitem{b7} Azathoth. (2018). “MyAnimeList Dataset”. Retrieved from: https://www.kaggle.com/azathoth42/myanimelist/version/5\#anime\_filtered.csv

\end{thebibliography}

\end{document}
